\begin{thebibliography}{1}

\bibitem{Enok} Novakovic, V., Hanssen, S.O., Thue, J.V., Wangensteen I., Gjerstad, F.O., et al.(2007) \textit{Energy management in buildings}. 3. Edition. Gyldendal Norsk Forlag AS 

\bibitem{ETP} International Energy Agency (2017) \textit{Energy Technology Perspectives 2017
Catalysing Energy Technology Transformations} %https://www.iea.org/buildings/

\bibitem{co2levels} Dlugokencky, E (5 February 2016). \textit{Annual Mean Carbon Dioxide Data}. Earth System Research Laboratory. National Oceanic \& Atmospheric Administration. Retrieved 30 september 2018

\bibitem{paris} United Nations (2015). \textit{Paris Agreement}

\bibitem{stats} International Energy Agancy (2017). \textit{Key world
energy statistics}.

\bibitem{temp} NASA's Goddard Institute for Space Studies (2017) \textit{GLOBAL LAND-OCEAN TEMPERATURE INDEX}.  Retrieved 30 september 2018 %https://climate.nasa.gov/vital-signs/global-temperature/

\bibitem{Ipcc}  Intergovernmental  Panel  on  Climate  Change (2018) \textit{SR 1.5}

\bibitem{Nhaps} Nature Publishing Group (2001). \textit{The National Human Activity Pattern Survey (NHAPS): a resource for assesing exposure to environmental pollutants}

\bibitem{uvalue} Ministry of Housing and Urban-Rural Development of the People's Republic of China (2005). \textit{Design Standard for Energy Efficiency of Public Buildings - GB 50189-2005}
% http://www.gbpn.org/databases-tools/bc-detail-pages/china-public#Energy%20Covered

\bibitem{energyplus} The U.S. Department of Energy’s (DOE) Building Technologies Office (BTO), managed by the National Renewable Energy Laboratory (NREL) \textit{EnergyPlus}

\bibitem{dahl} Dahl T., Albjerg N, et. al., (2010) \textit{Climate and Architecture}. Routledge. 

\bibitem{temp} Holiday weather % https://www.holiday-weather.com/shanghai/averages/

\end{thebibliography}
